Imposing a Weight Norm Constraint for Neuro-Adaptive Control

### 2025-06-17 presentation/presentation.tex
ppt update

% Inbuilt themes in beamer
\documentclass[8pt, aspectratio=169]{beamer}

@@

\usepackage{multirow}

% \usepackage{calc}
% \usepackage{svg}
% \usepackage{media9}             %pdflatex, latex+dvips+ps2pdf, xelatex
% \usepackage{multimedia}
% \usepackage{animate}

@@

% \logo{
%   \vspace{-.7cm}%
%   \includegraphics[height=0.3cm]{assets/kaist_logo.png}
%   \includegraphics[height=0.3cm]{assets/MIC_Lab_logo.png}
%   \hspace{.6cm}%
%   }

@@

% Title page frame
% \begin{frame}
\titlepage 
% \end{frame}

@@

% Lists frame
\section{Background and Contributions}

@@

  \textbf{Advantages of Neuro-Adaptive Control}
  \small{
    \begin{itemize}
      \item \textbf{Adaptability}: NAC adapts to changing environments and system dynamics.
      \item \textbf{Stability Guarantee}: The closed-loop stability is ensured using \textit{Lyapunov stability theory}.
      \item \textbf{Online Learning Capability}: NAC adapts in \textit{real-time} to new data with stability guarantees.
      \item \textbf{Robustness}: NAC handles \textit{uncertainties and disturbances} effectively with adaptive control techniques.
    \end{itemize}
  }

@@

  \textbf{Challenges}
  \small{
    \begin{itemize}
      \item \textbf{Optimality}: In general, the adaptation laws are driven with respect to the tracking error, which may not guarantee optimal performance.
      \item \textbf{Unpredictable Amplitude of Control input}: 
        \begin{itemize}
          \item The maximum amplitude of the NN weights is not predictable.
          \item This can result in unpredictable amplitude of the control input, which may lead to control saturation.
        \end{itemize}
      \item \textbf{Parameter Dependency}: 
      \begin{itemize}
        \item The performance of the NAC is highly dependent on the choice of parameters, such as learning rate and NN architecture.
      \end{itemize}
    \end{itemize}
  }

@@

% \subsection{Literature Review}

% \begin{frame}{\insertsubsectionhead}{Boundedness of NN Weights}

%   In general, the NN outputs are bounded by limiting the maximum amplitude of the NN weights.

%   \begin{enumerate}
%     \begin{columns}[T,onlytextwidth]
%         \column{0.49\textwidth}
%           \item \textbf{Projection Operator}

%           \begin{itemize}
%             \item Cats 
%             \item Dogs 
%             \item Birds
%           \end{itemize}

%         \column{0.49\textwidth}
%           \begin{figure}
%             \includegraphics[width=0.4\textwidth]{figures/KAIST-hi.png}
%           \end{figure}
%       \end{columns}

%       \begin{columns}[T,onlytextwidth]
%         \column{0.49\textwidth}
%           \item \textbf{$\epsilon$-modification, and $\sigma$-modification}

%           \begin{itemize}
%             \item Cats 
%             \item Dogs 
%             \item Birds
%           \end{itemize}

%         \column{0.49\textwidth}
%           \begin{figure}
%             \includegraphics[width=0.4\textwidth]{figures/KAIST-hi.png}
%           \end{figure}
%       \end{columns}
%   \end{enumerate}
% \end{frame}

% \begin{frame}{\insertsubsectionhead}{Input Saturation}

%   The input saturation is generally handled using an auxiliary system.

%   \begin{enumerate}
%     \begin{columns}[T,onlytextwidth]
%         \column{0.49\textwidth}
%           \item \textbf{Auxiliary Systems}

%           \begin{itemize}
%             \item Cats 
%             \item Dogs 
%             \item Birds
%           \end{itemize}

%         \column{0.49\textwidth}
%           \begin{figure}
%             \includegraphics[width=0.4\textwidth]{figures/KAIST-hi.png}
%           \end{figure}
%       \end{columns}

%       \begin{columns}[T,onlytextwidth]
%         \column{0.49\textwidth}
%           \item \textbf{Second?}

%           \begin{itemize}
%             \item Cats 
%             \item Dogs 
%             \item Birds
%           \end{itemize}

%         \column{0.49\textwidth}
%           \begin{figure}
%             \includegraphics[width=0.4\textwidth]{figures/KAIST-hi.png}
%           \end{figure}
%       \end{columns}
%   \end{enumerate}
% \end{frame}

\subsection{Research Objectives}

@@

  \textbf{Objective 1: Optimality}
  \begin{itemize}
    \item Formulate a constrained optimization problem to minimize the tracking error.
    \item Guarantee the stability of the system and the NN weights.
  \end{itemize}

  \textbf{Objective 2: Stability}
  \begin{itemize}
    \item Derive an adaptation law that guarantees the stability of the system.
    \item Ensure that the NN weights remain bounded during operation.
  \end{itemize}

  \textbf{Objective 3: Boundedness of }
  \begin{itemize}
    \item Ensure the controller is robust to uncertainties and disturbances.
    \item Validate the proposed method through numerical simulations.
  \end{itemize}

@@

\section{Proposed Method}

@@

  For the dual problem, 
  \begin{equation}
    \min_{\estwth}\max_{[\lambda_j]_{j\in\mathcal{I}}} 
    L(\mv{r},\estwth,[\lambda_j]_{j\in\mathcal{I}})
    ,
  \end{equation}
  the first-order gradient descent/ascent method is used to derive the adaptation law.

@@

@@

@@

\section{Experimental Validation}

@@

        \begin{equation}
          \qd
          =
          \begin{bmatrix}
              {q_d}_1\\
              {q_d}_2
          \end{bmatrix}
          = 
          \begin{bmatrix}
              +\cos(
                  \tfrac{\pi}{2}t
              ) + 1 \\
              -\cos(
                  \tfrac{\pi}{2}t
              ) - 1 
          \end{bmatrix}
          .
      \end{equation}

@@

  % % \movie[width=3cm,height=2cm,poster]{}{overall.mp4}
  % \begin{figure}
  %   \centering
  %   \href{https://youtu.be/U5uDbJQkGY8}{
  %     \includegraphics[width=.1\textwidth]{figures/KAIST-hi.png}
  %   }
  % \end{figure}

  % \animategraphics[loop,width=4cm]{gifs/overall-}
  % \animategraphics[loop,width=4cm]{10}{gifs/overall-}{0}{10}

@@

@@

\section{Conclusion}

>>>>

% Inbuilt themes in beamer
\documentclass[8pt, aspectratio=169, handout]{beamer}
% \documentclass[8pt, aspectratio=169]{beamer}

@@

\usepackage{multirow}
\usepackage{media9}

@@

@@

% Title page frame
\titlepage

@@

% ╔═══════════════════════════════════════════════╗
% ║ Section: Background and Contributions         ║
% ╚═══════════════════════════════════════════════╝
\section{Background and Contributions}

@@

  \textbf{Advantages of Neuro-Adaptive Control}
  \small{
    \begin{itemize}
      \item <+-> \textbf{Adaptability}: NAC adapts to changing environments and system dynamics.
      \item <+-> \textbf{Stability Guarantee}: The closed-loop stability is ensured using \textit{Lyapunov stability theory}.
      \item <+-> \textbf{Online Learning Capability}: NAC adapts in \textit{real-time} to new data with stability guarantees.
      \item <+-> \textbf{Robustness}: NAC handles \textit{uncertainties and disturbances} effectively with adaptive control techniques.
    \end{itemize}
  }

@@

  \begin{enumerate}
    \begin{columns}[T,onlytextwidth]
        \column{0.49\textwidth}
          \item \textbf{Weight Boundedness:}

          \begin{itemize}
            \item The NN weights can grow unbounded, leading to instability.
            \item Unbounded weights can cause the NN to produce large control inputs, which may lead to following challenges.
          \end{itemize}

        \column{0.49\textwidth}
          \centering
          \begin{figure}
            \includegraphics[width=0.4\textwidth]{figures/KAIST-hi.png}
            \caption{Unbounded NN weights.}
          \end{figure}
      \end{columns}

      \begin{columns}[T,onlytextwidth]
        \column{0.49\textwidth}
          \item \textbf{Unpredictable Amplitude of Control Input:}

          \begin{itemize}
            \item The NN outputs are unpredictable and not interpretable.
            \item This feature and unbounded NN weights can lead to control input saturation.
          \end{itemize}

        \column{0.49\textwidth}
          \centering
          \begin{figure}
            \includegraphics[width=0.8\textwidth]{figures/unpredictable.drawio.pdf}
            \caption{Unpredictable amplitude of NN outputs.}
          \end{figure}
      \end{columns}
  \end{enumerate}

@@

\subsection{Literature Review}

@@

  \begin{enumerate}
    \begin{columns}[T,onlytextwidth]
        \column{0.65\textwidth}
          \item \textbf{Projection Operator} \small{\textit{for weight boundednss}}

          \begin{itemize}
            \item Projects the NN weights onto a convex set.
            \item Ensures that the weights remain within a predefined bound.
          \end{itemize}

          \begin{equation}
            \estwth \leftarrow \myproj_{\overline{\theta}}(\estwth)
          \end{equation}

        \column{0.35\textwidth}
          \begin{figure}
            \includegraphics[width=0.3\textwidth]{figures/KAIST-hi.png}
          \end{figure}
      \end{columns}

      \vspace{0.2cm}

      \begin{columns}[T,onlytextwidth]
        \column{0.65\textwidth}
          \item \textbf{$\epsilon$-modification, and $\sigma$-modification} \small{\textit{for weight boundednss}}

          \begin{itemize}
            \item Add a stabilizing term to adaptation law.
            \item Invariance set of the NN weights can be ensured.
          \end{itemize}

          \begin{equation}
            \ddtt{\estwth} \leftarrow \ddtt{\estwth} - \rho \norm{\estwth}
          \end{equation}

        \column{0.35\textwidth}
          \begin{figure}
            \includegraphics[width=0.3\textwidth]{figures/KAIST-hi.png}
          \end{figure}

      \vspace{0.2cm}

      \begin{columns}[T,onlytextwidth]
        \column{0.65\textwidth}
          \item \textbf{Additional Control Inputs} \small{\textit{for control saturation}}

          \begin{itemize}
            \item Conventional controllers are used to address control input saturation. 
                  \begin{itemize}
                    \item Barrier Lyapunov function or auxiliary system-based control inputs.
                  \end{itemize}
            \item These methods do not guarantee the stability of the system.     
          \end{itemize}

        \column{0.35\textwidth}

          \begin{figure}
            \includegraphics[width=0.3\textwidth]{figures/KAIST-hi.png}
          \end{figure}

      \end{columns}
  \end{enumerate}
\end{frame}

\begin{frame}{\insertsubsectionhead}{Limitations of Existing Methods}

  \textbf{Limitation 1: Lack of Optimality}
  \begin{itemize}
    \item The existing methods do not guarantee the optimality of the control input.
    \item ...
  \end{itemize}

  \textbf{Limitation 2: Disruption of Learning Process by Additional Control Inputs}
  \begin{itemize}
    \item Feedback tracking error for learning is disrupted by additional control inputs.
      \begin{itemize}
        \item The feedback error does not reflect the error induced by the NN, directly.
      \end{itemize}  
    \item 
  \end{itemize}

@@

\subsection{Contributions}

  \textbf{Contribution 1: Unified Optimization Framework} 
  \begin{itemize}
    \item 
  \end{itemize}

  \textbf{Contribution 2: Online Learning Capability (Stabiltiy Guarantees)}
  \begin{itemize}
    \item 
  \end{itemize}

  \textbf{Contribution 3: Weight and Control Input Constraint Handling}
  \begin{itemize}
    \item 
  \end{itemize}

% ╔═══════════════════════════════════════════════╗
% ║ Section: Proposed Method                      ║
% ╚═══════════════════════════════════════════════╝
\section{Proposed Method}

@@

  To solve the dual problem, 
  \begin{equation}
    \min_{\estwth}\max_{[\lambda_j]_{j\in\mathcal{I}}} 
    L(\mv{r},\estwth,[\lambda_j]_{j\in\mathcal{I}})
    ,
  \end{equation}
  the first-order gradient descent/ascent method is used to derive the adaptation law.

@@

  \centering
  \begin{minipage}{.9\textwidth}

@@

  \end{minipage}

  \vspace{.2cm}

@@

% ╔═══════════════════════════════════════════════╗
% ║ Section: Experimental Validation              ║
% ╚═══════════════════════════════════════════════╝
\section{Experimental Validation}

@@

        \begin{equation}
          \qd
          =
          \begin{pmatrix}
              {q_d}_1\\
              {q_d}_2
          \end{pmatrix}
          = 
          \begin{pmatrix}
              +\cos(
                  \tfrac{\pi}{2}t
              ) + 1 \\
              -\cos(
                  \tfrac{\pi}{2}t
              ) - 1 
          \end{pmatrix}
          .
      \end{equation}

@@

@@

%   \centering
%   \includemedia[
%       width=0.96\linewidth,
%       height=0.54\linewidth,
%       activate=onclick,
%       addresource=demonstration.mp4,
%       flashvars={
%          source=demonstration.mp4
%         &autoPlay=true
%         &loop=true
%       }
%     ]{}{VPlayer.swf}

@@

% ╔═══════════════════════════════════════════════╗ 
% ║ Section: Conclusion and Future Work           ║
% ╚═══════════════════════════════════════════════╝
\section{Conclusion}
